A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-09-30 algorithm.Rmd
New title

---
title: A Hexagon Tile Map Algorithm For Spatial Mapping To Create Alternative Australian Maps
author:
  # see ?rjournal_article for more information
  - name: Stephanie Kobakian
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  stephanie.kobakian@monash.edu 
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  dicook@monash.edu 
abstract: >
  This algorithm creates a tessellated hexagon display to represent a set of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. The algorithm creates a display that showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
preamble: |
  % Any extra LaTeX you need in the preamble
bibliography: sugarbag.bib
output: rticles::rjournal_article
---

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/aus_melanoma_p.pdf}
\caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/qld_grid.pdf}
\caption{\label{fig:qld_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

\begin{figure}
\includegraphics[width=14cm]{figures/flowchart.pdf}
\caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/aus_gghexmap.pdf}
\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/1centroids.pdf}
\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Queensland at Level 2. The points show the locations of the centroids of the SA2 areas.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/2grid.pdf}
\caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=10cm]{figures/3grid.pdf}
\caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied. The blue dots show the grid points left to choose from after the buffer step.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/4grid.pdf}
\caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/5allocate.pdf}
\caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/6allocate.pdf}
\caption{\label{fig:buffs}A complete hexagon tile map of Queensland.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/7SIR.pdf}
\caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map. The colour of each Statistical Area of Australian at Level 2 coloured by SIR. A choropleth map (a) of SIR is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/aus_gghexmap.pdf}
\caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red).}
\end{figure}

>>>>

---
title: A Hexagon Tile Map Algorithm for Displaying Spatial Data
author:
  # see ?rjournal_article for more information
  - name: Stephanie Kobakian
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  stephanie.kobakian@monash.edu 
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  dicook@monash.edu 
abstract: >
  This algorithm creates a tessellated hexagon display to represent a set of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. The algorithm creates a display that showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
preamble: |
  % Any extra LaTeX you need in the preamble
bibliography: sugarbag.bib
output: rticles::rjournal_article
---

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/aus_melanoma_p.pdf}
\caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/qld_grid.pdf}
\caption{\label{fig:qld_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

\begin{figure}
\includegraphics[width=14cm]{figs/flowchart.pdf}
\caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/1centroids.pdf}
\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Queensland at Level 2. The points show the locations of the centroids of the SA2 areas.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figs/2grid.pdf}
\caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=10cm]{figs/3grid.pdf}
\caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied. The blue dots show the grid points left to choose from after the buffer step.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figs/4grid.pdf}
\caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figs/5allocate.pdf}
\caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figs/6allocate.pdf}
\caption{\label{fig:buffs}A complete hexagon tile map of Queensland.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/7SIR.pdf}
\caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map. The colour of each Statistical Area of Australian at Level 2 coloured by SIR. A choropleth map (a) of SIR is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
\caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red).}
\end{figure}
